Hydrodynamics and rheology of adhesive vesicle doublets

### 2019-02-11 vesicle_code/docs/adhesion/adhesion.tex
working on extensional

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
point (zero-velocity at the origin) in an extensional flow, $\uu =\chi(-x,y)$,
is a saddle point where two laminar streams converge along an axis and
then diverge in the orthogonal direction.  With an active control algorithm
to place the stagnation point at a desirable location by adjusting the streaming
flow strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
particle can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as particle
image velocimetry of flow inside and around the particle.  To explore
the application of such a fluid trap to measure the adhesion strength
between two bound vesicle membranes, we propose the following thought
experiment.

@@

We begin with two identical vesicles forming a doublet under an
adhesion potential in a quiescent flow as described in
Section~\ref{sec:qflow}.  Once a doublet forms and reaches an
equilibrium configuration, we turn on the fluid trap with the stagnation
point placed at the center of the vesicle doublet, which has a flat contact region as shown in \S~\ref{sec:qflow}. 
Based on how the contact region aligns with the extensional flow, 
we can define the inclination angle of the vesicle doublet as illustrated in Figure~\ref{fig:InclinationAngle}.
%

When $\theta=\pi$ (the doublet long axis is aligned with the far-field diverging flow), the converging flow
pushes vesicles towards each other and the short-range repulsive force is essential to keep the two vesicles at the separation distance.
With the converging flow pushing the two vesicles towards the stagnation point dynamically placed at the doublet center, 
this configuration is expected to be more stable than the $\theta=\pi/2$ configuration in the middle of Figure~\ref{fig:InclinationAngle},  where  
the doublet long axis is parallel to the converging direction. This is because
when $\theta=\pi/2$ the diverging flow is pulling the vesicles away from each other as shown in the illustration. 
If the doublet inclination angle is fixed at $\theta=\pi/2$,
the vesicle doublet stays intact only when the adhesive force is strong enough to dominate over the fluid drag in this configuration.
Thus it is possible that the diverging flow may overcome adhesion and
break up the doublet. It is also reasonable to expect a vesicle doublet to rotate from $\theta=\pi/2$ to $\theta=\pi$,
such that the fluid flow is pushing them together rather than pulling them apart.

In the following numerical experiments we place a vesicle doublet with $\theta=\pi/2$, so that
the diverging flow may be strong enough to pull vesicles away from the doublet.
%In this configuration the flow is pulling the vesicles away from each other, and 
%is expected to be less stable than the $\theta=\pi$ configuration where the fluid flow is constantly pushing vesicles towards each other. 
%
At low extensional
rates, we expect the $\theta=\pi/2$ doublet to stay bound at the fluid
trap stagnation point.  On the other hand, the vesicle doublet may
become unstable and eventually separate at higher extensional rates.
Thus we expect there to exist a critical extensional rate $\chi_c$ above which
the vesicle doublet cannot stay bound under a given adhesion potential.
Therefore, the dependence of the critical extensional rate $\chi_c$ on the
adhesion potential and the mechanical vesicle properties provides a
means to probe the physics of membrane adhesion.

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
point can be controlled in an experimental
setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control
algorithm in the microfluidic experiments by moving the center of the
doublet at each time step so that the stagnation point occurs exactly in
the middle of the doublet.  
With this adjustment, the vesicles either
remain as a doublet in the fluid trap centered around the stagnation
point, or the doublet is broken and the vesicles separate from one
another.

In Figures~\ref{fig:extensional1},
snapshots of a fluid trap containing a vesicle doublet of reduced area
$\Delta A = 0.7$ are simulated at different extensional rates.  While
this doublet remains bound for all the
considered extensional rates, a doublet with a reduced area of $\Delta A
= 0.8$ is split with a critical extensional rate $\chi_c =0.1$
(bottom row in Figure~\ref{fig:extensional3}).  
%
\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.  The
  reduced area $\Delta A = 0.7$, the Hamaker constant $\mathcal{H} =
  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
  rate $\chi = 0.02$ ({\em top}) and $\chi=0.7$ ({\em bottom}).  The center of the vesicle, denoted with a
  black square, is a stagnation point.}
  \end{figure}
  %
  For extensional rates and reduced areas that result in a bound vesicle doublet, 
we observe that the doublet always rotate from $\theta=\pi/2$ configuration towards
the more stable $\theta=\pi$ configuration, as shown in Figures~\ref{fig:extensional1}--\ref{fig:extensional3}.
We also observe that in most cases with moderate extensional flow rates the doublet falls short of 
aligning their long axis with the diverging direction.

%  \begin{figure}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png}
%  \caption{\label{fig:extensional2} A doublet inside a fluid trap.  The
%  reduced area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H}
%  = 0.7$, the adhesion length scale is $\delta = 0.4$, and the
%  extensional rate is $\chi = 0.07$.  The center of the vesicle, denoted
%  with a black square, is a stagnation point.}
%  \end{figure}

 \begin{figure}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}\\
    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.
  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant $\mathcal{H} =
  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
  rate $\chi = 0.1$.  The center of the vesicle, denoted with a black
  square, is a stagnation point.}
  \end{figure}

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (middle).  We observe that not
only do larger smaller extensional rates result in smaller inclination
angles, but smaller reduced areas also result in smaller inclination
angles.  Moreover, the critical Hamaker constant that determines if the
doublet remains trapped or is broken decreases with an increasing
extensional rate.
%\begin{figure}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
%  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
%  \caption{\label{fig:extensional4} A doublet broken by an extensional
%  flow.  The reduced area is $\Delta A = 0.8$, the Hamaker constant is
%  $\mathcal{H} = 0.7$, the adhesion length scale is $\delta = 0.4$, and
%  the extensional rate is $\chi = 0.1$.  Initially, the doublet tilts to
%  an inclination angle, and then the extensional rate overcomes the
%  adhesive force and the doublet is broken.  The center of the vesicle,
%  denoted with a black square, is a stagnation point.}
%\end{figure}
We summarize the final inclination angle of the
doublet in the right plot of Figure~\ref{fig:extensionalInclinationAngle}.
The size of the round dots are scaled to the final inclination angle as
defined in the right plot.  At smaller extensional rates, the vesicles
come closer to aligning their long axis with the diverging direction.
When the doublet is broken at reduced area $\Delta A = 0.80$, the
extensional rate is sufficiently large to align the long axis of the
vesicle with the diverging direction and then the vesicles separate
(bottom row in Figure~\ref{fig:extensional3}).  For very low extensional rates, the
time horizon is insufficient for the doublet to reach an equilibrium
state, and these simulations are marked with a square.
%
The right plot of Figure~\ref{fig:extensionalInclinationAngle} 
also summarizes the  reduced areas and
extensional rates that result in a bound vesicle doublet in a fluid trap: Parameter values with a blue
mark result in a fluid trap and parameter values with a red mark result
in vesicle separation.

%\begin{figure}[htp]
%  \begin{minipage}{0.53\textwidth}
%    \includegraphics[width=0.33\textwidth]{figs/angleDefinition.pdf} \:
%    \includegraphics[width=0.34\textwidth]{figs/rotate1.pdf} \:
%    \includegraphics[width=0.26\textwidth]{figs/rotate2.pdf}
%  \end{minipage}
%  \hfill
%  \begin{minipage}{0.45\textwidth}
%    \centering
%    \includegraphics[width=0.8\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
%  \end{minipage}
%  \caption{\label{fig:extensionalPhaseDiagram}  A phase diagram of the long-time
%  behavior of a fluid trap formed by two adhering vesicles in an
%  extensional flow.  The Hamaker constant is $\mathcal{H}=0.7$ and the
%  adhesion length scale is $\delta = 0.4$.  For small extensional rates,
%  the doublet structure is not broken (blue marks), while at large
%  extensional rates, the doublet is broken (red marks).  The size of the
%  round blue marks indicates the final inclination angle with the larger
%  dots rotating less ($\theta=\pi$) and the smaller dots rotating more
%  ($\theta = \pi/2$).  A square mark is used for simulations that did
%  not result in an equilibrium inclination angle in the given time
%  horizon.}
%\end{figure}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
The hydrodynamics of a single vesicle in an extensional flow has
revealed novel nonlinear vesicle dynamics not found for a viscous
drop~\cite{KantslerSegreSteinberg2008_PRL, ZhaoShaqfeh2013_JFM,
Narsimhan2014_JFM, DahlNarsimhanGouveia2016_SoftMatt}.  The stagnation
point (zero-velocity at the origin) in an extensional flow, $\uu =\chi(-x,y)$,
is a saddle point where two laminar streams converge along an axis and
then diverge in the orthogonal direction.  With an active control algorithm
to place the stagnation point at a desirable location by adjusting the streaming
flow strength with a feedback loop~\cite{Johnson-Chavarria2011_EMJ}, a
particle can be trapped at the stagnation point for long time scales to
facilitate image acquisition or other detailed measures such as particle
image velocimetry of flow inside and around the particle.  To explore
the application of such a fluid trap to measure the adhesion strength
between two bound vesicle membranes, we propose the following thought
experiment.  Beginning with two identical vesicles in an equilibrium
configuration that form a doublet with a flat contact region
(Figure~\ref{fig:Dec18_vesicle_shape}), we turn on the fluid trap with
the stagnation point placed at the center of the vesicle doublet.
Depending on the Hamaker constant, we expect that either the flow
overcomes the adhesive force and the doublet is broken, or the adhesive
force dominates and the doublet reaches a stable stationary
configuration.

@@

In the following numerical experiments we initially place a vesicle
doublet with $\theta=\pi$, so that the diverging flow may be strong
enough to pull vesicles away from the doublet.  At low extensional
rates, we expect the doublet to stay bound at the fluid trap stagnation
point.  On the other hand, the vesicle doublet may become unstable and
eventually separate at higher extensional rates.  Thus we expect there
to exist a critical extensional rate $\chi_c$ above which the vesicle
doublet cannot stay bound under a given adhesion potential.  Therefore,
the dependence of the critical extensional rate $\chi_c$ on the adhesion
potential and the mechanical vesicle properties provides a means to
probe the physics of membrane adhesion.

Based on how the contact region aligns with the extensional flow, we can
define the inclination angle of the vesicle doublet as illustrated in
Figure~\ref{fig:InclinationAngle}. When $\theta=\pi$ (the doublet long
axis is aligned with the far-field converging flow), the diverging flow
pulls the vesicles apart from each other and the short-range repulsive
force is essential to keep the two vesicles from separating.  In
contrast, when $\theta = \pi/2$ (the doublet long axis is aligned with
the diverging flow), the converging flow pushes the vesicles towards
each other and the short-range repulsive force is essential to keep the
two vesicles at the separation distance.  With the converging flow
pushing the two vesicles towards the stagnation point dynamically placed
at the doublet center, this configuration is expected to be more stable
than the $\theta=\pi$ configuration in the left of
Figure~\ref{fig:InclinationAngle}, where the doublet long axis is
parallel to the converging direction. This is because when $\theta=\pi$
the diverging flow is pulling the vesicles away from each other as shown
in the illustration.  If the doublet inclination angle is fixed at
$\theta=\pi/2$, the vesicle doublet stays intact only when the adhesive
force is strong enough to dominate over the fluid drag in this
configuration \todo[inline]{I don't follow this sentence}.  Thus it is
possible that the diverging flow may overcome adhesion and break up the
doublet. It is also reasonable to expect a vesicle doublet to rotate
from $\theta=\pi$ to $\theta=\pi/2$, such that the fluid flow is pushing
them together rather than pulling them apart.

We consider vesicle doublets with reduced areas 0.70, 0.75, 0.80, 0.85,
0.90, and 0.95, all with a length of $2\pi$, and we vary the extensional
rate, $\chi$, between $10^{-2}$ and $10^{-1}$.  Since the stagnation
point can be controlled in an experimental
setting~\cite{Johnson-Chavarria2011_EMJ}, we mimic the active control of
the microfluidic experiments by moving the center of the doublet at each
time step so that the stagnation point occurs exactly in the middle of
the doublet.  With this adjustment, the vesicles either remain as a
doublet in the fluid trap centered around the stagnation point, or the
doublet is broken and the vesicles separate from one another.

In Figures~\ref{fig:extensional1}, snapshots of a fluid trap containing
a vesicle doublet of reduced area $\Delta A = 0.7$ are simulated at
three different extensional rates.  While this doublet remains bound for
all the considered extensional rates, a doublet with a reduced area of
$\Delta A = 0.8$ is split with a critical extensional rate $\chi_c =0.1$
(Figure~\ref{fig:extensional3}).  For extensional rates and reduced
areas that result in a bound vesicle doublet, we observe that the
doublet always rotates from $\theta=\pi$ configuration towards the more
stable $\theta=\pi/s$ configuration, as shown in
Figures~\ref{fig:extensional1}.  We also observe that in most cases with
moderate extensional flow rates the doublet falls short of aligning
their long axis with the diverging direction.

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi2em2_ra070_image05.png}\\
   \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi7em2_ra070_image05.png} \\
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra070_image05.png}
  \caption{\label{fig:extensional1} A vesicle doublet in an extensional
  flow with an initial inclination angle $\theta=\pi/2$.  The reduced
  area is $\Delta A = 0.7$, the Hamaker constant is $\mathcal{H} = 0.7$,
  the separation distance is $\delta = 0.4$, and the extensional rate is
  $\chi = 0.02$ ({\em top}), $\chi=0.07$ ({\em middle}), and $\chi =
  0.1$ ({\em bottom}).  The center of the vesicle, denoted with a black
  square, is a stagnation point.}
  \end{figure}

 \begin{figure}
    \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth,trim={4cm 2cm 4cm 1cm},clip]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \caption{\label{fig:extensional3} A vesicle doublet in an extensional flow with an initial inclination angle $\theta=\pi/2$.
  The reduced area $\Delta A = 0.7$ ({\em top}) and $\Delta A=0.8$ ({\em bottom}). The Hamaker constant $\mathcal{H} =
  0.7$, the adhesion length scale $\delta = 0.4$, and the extensional
  rate $\chi = 0.1$.  The center of the vesicle, denoted with a black
  square, is a stagnation point.}
  \end{figure}

In Figure~\ref{fig:extensionalInclinationAngle}, we plot the inclination
angle of the doublet as a function of time for four different
extensional rates (left) and the final inclination angle for all
doublets that reach an equilibrium state (middle).  We observe that not
only do larger smaller extensional rates result in smaller inclination
angles, but smaller reduced areas also result in smaller inclination
angles.  Moreover, the critical Hamaker constant that determines if the
doublet remains trapped or is broken decreases with an increasing
extensional rate.

We summarize the final inclination angle of the doublet in the right
plot of Figure~\ref{fig:extensionalInclinationAngle}.  The size of the
round dots are scaled to the final inclination angle as defined in the
right plot.  At smaller extensional rates, the vesicles come closer to
aligning their long axis with the diverging direction.  When the doublet
is broken at reduced area $\Delta A = 0.80$, the extensional rate is
sufficiently large to align the long axis of the vesicle with the
diverging direction and then the vesicles separate (bottom row in
Figure~\ref{fig:extensional3}).  For very low extensional rates, the
time horizon is insufficient for the doublet to reach an equilibrium
state, and these simulations are marked with a square.  The right plot
of Figure~\ref{fig:extensionalInclinationAngle} also summarizes the
reduced areas and extensional rates that result in a bound vesicle
doublet in a fluid trap: Parameter values with a blue mark result in a
fluid trap and parameter values with a red mark result in vesicle
separation.
